### 2021-09-17 README.Rmd
Initial depletion now operational. No EWN

@@

* 2021-09-10 aMSE 0.0.0.100 Many small, but significant, changes. Modified getdata which interacts with the ###HS.R file and added the
zoneDP$NAS data input. Added a summary recdev plot to condition tab.

* 2021-09-03 aMSE 0.0.0.200 Lots of tidying of help pages, added numbersatsizeSAU. Added a fixed TasmanianHS.R file to the data-raw directory.

>>>>

* 2021-09-17 aMSE 0.0.0.050 Finalized details of the optional initial depletion. Amended the logistic function so it now works when using the knifeedge option!

@@
